IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-13 ms.tex
I added some stand-in affiliations and one example reference.
I added the discovery references for 2MASS J1821 and 2MASS J0835.

\usepackage{natbib}
\bibliographystyle{astroads}

@@

\author{E. Schlawin, T. Karalidi?}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

\author{A. Burgasser, J. Teske, J. Gizis}
\affil{B}

@@

\section{Introduction}

>>>>

\usepackage{natbib}

@@

\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi? }
\affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
\email{eas342@email.arizona.edu}

@@

\section{Introduction}
\citep{burgaser2014irtf}.

We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J1821+14010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J0835-019 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.

\section{Observations}
